Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-14 main.Rmd
todo additions made

\todo[inline]{What is g-rel? - g-rel can be any granularity relationships like -   
groups into, finer than, groups periodically (the granularity relationships defined in this paper) or sub-granular, shift equivalent (not discussed in this paper but other relationships that the author discussed in @Bettini1998-ed)}

Given the set of all granularities defined over the time domain $(Z; <)$, and the granularity relationship $\trianglelefteq$ (groups into), the granularity mapping each index into the corresponding instant (same integer number as the index) is a bottom granularity with respect to $\trianglelefteq$.

@@

@@

\todo[inline]{What does "full-integer" mean? It might be the case that we do not always
have integers as the label sets of granularities. A full-integer labeled granularities are defined in definition 2 since labels coincide with indices. These labels can be an
arbitrary subset of (possibly non contiguous) integers and could be used to identify granules. The author has introduced the definition of "labeled granularity" in @Ning2002-tf which could be added after definition of linear granularity to clarify this. }

@@

where $\text{second}(1)$ would start a minute and likewise.

\todo[inline]{What does this last phrase mean? - if  the time horizon is such that it starts from the 15th second of a day, then doing repeated operations of grouping might result in a granule of "resultant" granularity day or week, which is different from a time-stamped day or week. Could be phrased better or deleted.}

When the granules for second and minutes are arranged, the first granule of seconds and minutes granules should that overlap share elements from the underlying time domain}

@@

For example, due to the uneven length of months, we need to use the altering-tick operation to compute months from days.
\begin{align*}
\text{pseudomonth} = &\text{Alter}^{12}_{11,-1}(\text{day}, \\
  &~~\text{Alter}^{12}_{9,-1}(\text{day}, \\
  &~~~~\text{Alter}^{12}_{6,-1}(\text{day}, \\
  &~~~~~~\text{Alter}^{12}_{4,-1)}(\text{day}, \\
  &~~~~~~~~\text{Alter}^{12}_{(2,-3)}(\text{day}, \\
  &~~~~~~~~~~\text{Group}_{31}(\text{day})))))),
\end{align*}
where the granularity pseudomonth is generated by grouping 31 days, and then shrink April (4), June (6), September (9) and November (11) by 1 day, and shrink February (2) by 3 days [@Ning2002-tf].

\todo[inline]{Why is this called a ``pseudomonth''? - Here,  granularity pseudomonth is generated by grouping 31 days, and then shrink April, June, September and
November by 1 day, and shrink February (2) by 3 days. It doesn't incorporate adjustments for leap year or seconds in which case the period for the altering operation should be 400 instead of 12. ``pseudomonth`` computes months only in non-leap years.}

>>>>

Here, g-rel could be any relationship defined between granularities like "groups into", "finer than" or "groups periodically". Given the set of all granularities defined over the time domain $(Z; <)$, and the granularity relationship $\trianglelefteq$ (groups into), the granularity mapping each index into the corresponding instant (same integer number as the index) is a bottom granularity with respect to $\trianglelefteq$.

@@

<!-- It might be the case that we do not always have integers as the label sets of granularities.  -->

<!-- \begin{definition}[Labelled granularity]\label{def:labelgran} -->

The notion of labeled granularity is introduced in @Bettini2000-qk to simplify the calendar algebra. A labeled granularity is a pair $(\L, G)$, where $L$ is a subset of the integers, and $G$ is a mapping from $L$ to the subsets of the time domain such that (1) if $i<j$ , where $i$ and $j$ are in $L$, and $G(i)$ and $G(j)$ are non-empty, then each element in $G(i)$ is less than all the elements of $G(j)$, and (2) if $i<k<j$ , where $i$, $j$ , and $k$ are in $L$, and $G(i)$ and $G(j)$ are non-empty, then $G(k)$ is non-empty. $L$ is called the label set of $G$. When $L$ is exactly the integers, the granularities are called full-integer labeled granularity like the one defined in Definition \ref{def:linear}. However, the set $L$ of labels can be an arbitrary subset of (possibly non contiguous) integers and could be used to identify granules. Some calendar operations will only work on full-integer labeled granularities, while others could be implemented using more flexible labelings.

@@

@@

where $\text{second}(1)$ should coincide with $\text{minute}(1)$ and likewise. Otherwise, repeated operations of grouping might result in a granule of "resultant" granularity "day" or "week", which is different from a time-stamped "day" or "week".

@@

For example, due to the uneven length of months, we need to use the altering-tick operation to compute months from days.
Let us consider a granularity "pseudomonth" which computes months only for non-leap years.
\begin{align*}
\text{pseudomonth} = &\text{Alter}^{12}_{11,-1}(\text{day}, \\
  &~~\text{Alter}^{12}_{9,-1}(\text{day}, \\
  &~~~~\text{Alter}^{12}_{6,-1}(\text{day}, \\
  &~~~~~~\text{Alter}^{12}_{4,-1)}(\text{day}, \\
  &~~~~~~~~\text{Alter}^{12}_{(2,-3)}(\text{day}, \\
  &~~~~~~~~~~\text{Group}_{31}(\text{day})))))),
\end{align*}
where the granularity pseudomonth is generated by grouping 31 days, and then shrink April (4), June (6), September (9) and November (11) by 1 day, and shrink February (2) by 3 days [@Ning2002-tf].
